Decentralised Authoring, Annotations and Notifications for a Read-Write Web with dokieli

### 2017-04-07 index.tex
no plural
fixed grammar

\par 
                                \textbf{Decentralised authoring and annotation systems}:
                                Some authoring and publishing systems already go into a decentralised direction. However, they only realize a relatively small subset of the principles outlined in the last section. \textit{LibreOffice Online}, for example, allows collaborative editing of office documents (e.g., Writer) from the Web browser. Content can be stored under different CMSs in the cloud. The document’s interface consists of image tiles which are sent from the server and rendered in the browser. However, it hardly provides accessibility, rich interlinking and annotations or separations of concerns.

                                The \textit{Smallest Federated Wiki} pages to be forked and maintain personal copies.

>>>>

\par 
                                \textbf{Decentralised authoring and annotation systems}:
                                Some authoring and publishing systems already go into a decentralised direction. However, they only realize a relatively small subset of the principles outlined in the last section. \textit{LibreOffice Online}, for example, allows collaborative editing of office documents (e.g., Writer) from the Web browser. Content can be stored under different CMSs in the cloud. The document’s interface consists of image tiles which are sent from the server and rendered in the browser. However, it hardly provides accessibility, rich interlinking and annotations or separation of concerns.

                                The \textit{Smallest Federated Wiki} allows pages to be forked; users can maintain personal copies.
